---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Problem 2

Create a flexdashboard using plotly for that includes at least three distinct plot types (e.g. scatterplots, line plots, bar plots, box plots, etc.) using `Instacart` dataset from the `p8105.datasets` package.

Load packages and data:

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Import `Instacart` dataset and filter data:

```{r}
data("instacart")

instacart = 
  instacart %>%
  as_tibble(instacart) %>%
  janitor::clean_names() %>%
  select(add_to_cart_order, order_dow, order_hour_of_day, aisle)
```

## Plotly barplot: Number of items ordered in each aisle

This barplot reveals number of items ordered in each aisle, limiting to aisles with more than 5000 items ordered.

```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 5000) %>%
  mutate(
    aisle = fct_reorder(aisle, n),
    text_label = str_c("Aisle: ", aisle, "\nNumber of Orders: ", n)
  ) %>%
  plot_ly(x = ~aisle, y = ~n, color = ~aisle, type = "bar", text = ~text_label, colors = "viridis")
```

## Plotly scatterplot: Order hour of day for different types of Aisle sorted by weekday

This scatterplot shows 1000 randomly selected samples' order hour of day for different types of Aisle sorted by weekday.

```{r}
instacart %>%
  sample_n(1000) %>%
  group_by(aisle) %>%
  mutate(text_label = str_c("Aisle: ", aisle, "\nOrder Time: ", order_hour_of_day, ":00")) %>%
  plot_ly(
    x = ~aisle, y = ~order_hour_of_day, type = "scatter", mode = "markers",
    color = ~order_dow, text = ~text_label, alpha = 0.5)
```

## Plotly boxplot: Number of orders added to cart for each Aisle

This baxplot indicates 1500 randomly selected samples' number of orders added to cart for each Aisle.

```{r}
instacart %>%
  sample_n(1500) %>%
  mutate(aisle = fct_reorder(aisle, add_to_cart_order)) %>%
  plot_ly(y = ~add_to_cart_order, color = ~aisle, type = "box", colors = "viridis")
```